### 2014-08-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor fix to ambient temp.

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter                                                  & Description                                   & Discussion                            \\
\midrule
Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
                                                           &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                       \\
                                                           &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                       \\
                                                           &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{fire}}   \\ 
                                                           &  Porch Fire: 3.3~MW                           &                                       \\ [.25cm]                     
\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\
                                                           &  $\rho$: 510~kg/m$^3$                         &                                       \\
                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                       \\ [.25cm]
\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
                                                           &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
\normalsize
\end{table}

>>>>

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter                                                  & Description                                   & Discussion                            \\
\midrule
Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
Ambient Temperature$^*$                                    &  20~$^{\circ}$C (68~$^{\circ}$F)              & --                                    \\ [.1cm]
\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
                                                           &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                       \\
                                                           &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                       \\
                                                           &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{fire}}   \\ 
                                                           &  Porch Fire: 3.3~MW                           &                                       \\ [.25cm]                     
\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\
                                                           &  $\rho$: 510~kg/m$^3$                         &                                       \\
                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                       \\ [.25cm]
\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
                                                           &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
\normalsize
\end{table}
